Classification and characterization of anthropogenic plant communities in the northwestern Iberian Peninsula

### 2024-10-11 doc/title-page.Rmd
zenodo link ⛓️
revision for AVS

---
title: "Classification and characterization of anthropogenic plant communities at the ecoregion level"
output: 
  bookdown::word_document2:
    reference_docx: template.docx
    number_sections: false
bibliography: refs.bib
csl: journal-of-vegetation-science.csl
link-citations: yes
always_allow_html: true
---

@@

. Upon publication, a version of record of the repository will be deposited in Zenodo.

>>>>

---
title: "Classification and characterization of anthropogenic plant communities in the northwestern Iberian Peninsula"
output: 
  bookdown::word_document2:
    reference_docx: template.docx
    number_sections: false
bibliography: refs.bib
csl: journal-of-vegetation-science.csl
link-citations: yes
always_allow_html: true
---

@@
